Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
improved our abstract and introduction a little bit

Our contributions are as follows.
In \sect\ref{sec:Methodology},
we generalize buildings on a start map 
to obtain buildings on a smaller-scale goal map.
The generalization consists of aggregating, growing, and simplifying.
We aggregate buildings which will be too close at an output scale 
by introducing bridges.
We grow buildings by buffering,
where we use so-called \emph{miter} joins to keep the right angles of buildings.
Because of using this kind of joins instead of \emph{round} ones,
we have to be more careful.
We show how to solve the problems caused by miter joins.
Eventually, we manage to generate buildings at any intermediate scales.
We carry out a case study in \sect\ref{sec:CaseStudy}
and discuss the performances of our method.
We conclude our paper in \sect\ref{sec:Conclusion}.

>>>>

Our contributions are as follows.
In \sect\ref{sec:Methodology},
we continuously generalize a start map, of buildings, 
to a smaller-scale goal map.
The generalization consists of aggregating, growing, and simplifying.
We aggregate original buildings which will be too close at an output scale 
by introducing bridges.
We grow (bridged) original buildings by buffering,
where we use so-called \emph{miter} joins to keep the right angles of buildings.
Because of using this kind of joins instead of \emph{round} ones,
we have more problems.
We show how to solve these problems.
We also simplify the buildings at the output scale.
We carry out a case study 
and discuss the performances of our method in \sect\ref{sec:CaseStudy}.
We conclude our paper in \sect\ref{sec:Conclusion}.
